Generate Real and Pseudo-absences

### 2023-12-06 scripts/generate_absences.Rmd
flesh fn

@@

```{r Create simplified BLM surface management}

@@

```{r}
library(geosphere)

st_area(x, ...)

>>>>

```{r Create simplified BLM surface management, eval = F}
p1 <- '/media/steppe/hdd/geospatial/SMA_WM.gdb'

st_layers(p1)
ag <- st_read(p1, 'SurfaceMgtAgy_BLM') %>% 
  filter(ADMIN_ST != 'AK') %>% 
  rename(geometry = SHAPE) %>% 
  select(geometry) %>% 
  st_make_valid() %>% 
  st_union()

ag <- st_simplify(ag, dTolerance = 1000)
plot(ag)

pout <- '/media/steppe/hdd/SDM_restorations/data/raw/coarse_blm/'
st_write(ag, dsn = paste0(pout, 'coarse_surface.shp'))
```

@@

```{r load aim data for absences}

AIM_points <- st_read(dsn = p, layer = 'TerrADat', quiet = T) %>%
  select(PrimaryKey, DateVisited, geometry = Shape) %>% 
  st_transform(5070)

spp_richness <- st_read(dsn = p1, 
        layer = 'tblSpecRichDetail', quiet = T) %>% 
  select(SpeciesList, PrimaryKey) %>% 
  filter(SpeciesList %in% target_symbols) %>% 
  right_join(AIM_points, by = 'PrimaryKey') %>% 
  st_as_sf()

pout <- '/media/steppe/hdd/SDM_restorations/data/raw/coarse_blm/'
blm_surf <- st_read(paste0(pout, 'coarse_surface.shp'))
blm_surf <- st_simplify(blm_surf, dTolerance = 500) # just make it a bit smaller. 
```

```{r}

aim <- st_read('../data/raw/occurrence/AIM/AIM_records.shp') %>% 
  filter(SpcsLst == 'ACHY')

ob_hull <- absence_drawer(aim, bg_abs = 0.15)
buf_hull <- absence_drawer(aim, bg_abs = 0.15)
box_hull <- absence_drawer(aim, bg_abs = 0.15)
bbox <- absence_drawer(aim, bg_abs = 0.15)

ggplot() +
 # geom_sf(data = ob_hull, fill = NA) + 
#  geom_sf(data = buf_hull, fill = NA) + 
 # geom_sf(data = box_hull, fill = NA) +
  geom_sf(data = bbox, fill = 'red')

@@
